Black-hole ringdown as a probe of higher-curvature gravity theories

### 2022-03-08 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
hs:percentile reminder

In this formalism our QNM frequencies are expressed through functions,
%
\begin{subequations}
\begin{align}
\omega_k &= \omega_k(m_1, m_2, \chi_1, \chi_2,\ell, \{\delta \omega_k^{(j)}\})\\
\tau_k   &= \tau _k(m_1, m_2, \chi_1, \chi_2, \ell, \{\delta \tau_k^{(j)}\})
\end{align}
\end{subequations}
%
where the estimates of $(m_1,\, m_2,\, \chi_1,\, \chi_1)$ are used to predict the final mass and spin $(M_f,\, \chi_f)$ through~\cite{Taracchini:2013rva,Hofmann:2016yih}.
%
Additionally, $(\omega_k,\, \tau_k)$ depend on the coupling constant $\ell$
defined in Eq.~\eqref{eq:def_gamma} as well as the sets, $\{\delta \omega_k^{(j)}\},$ and
$\{\delta \tau_k^{(j)}\}$, where $j$ ranges from zero to the power of spin in Eqs.~\eqref{eq:kerr_expansion}
up to which we include corrections.
%
For example, if we restrict ourselves to corrections in the $j=0$, or $\chi_f^0$, terms for just the $k=(2,2,0)$ mode, then we would just have two additional degrees of freedom, $(\delta \omega_0^{(0)}, \delta \tau_0^{(0)})$. In this paper, we would restrict ourselves to corrections to the $j=0$ and $j=1$ terms, i.e., leading and next-to-leading order corrections to the spin, $\chi_f$.
%

@@

Just as in GR where the coefficients $\omega^{j}$, $\tau^{j}$ are determined by
comparison against the Kerr QNMs, a theory-specific calculation predicts the
numerical values of $\delta\omega^{(j)}$ and $\delta\tau^{(j)}$
%
This means that using the $\pSEOB$ waveform model with theory-specific informed
QNMs we reduce the parameters space of beyond-GR parameters to one, i.e., to
only $\gamma$, which in turn contains information about the length scale $\ell$.
%
It is important to emphasize that our procedure is different from that of Ref.~\cite{Carullo:2021dui}
which, for a given value of $p$, varied all $\ell$, $\delta\omega^{(i)}$ and $\delta\tau^{(i)}$ parameters.
%
% As we will see later, our theory-informed approach can result to stronger constraints to certain modified ....

@@

Among our beyond-GR parameters, $\{\ell, \delta \omega_k^{(j)}\delta \tau_k^{(j)}\}$, as already mentioned in the previous section, we would mostly hold $\{\delta \omega_k^{(j)}\},$ and $\{\delta \tau_k^{(j)}\}$ fixed to theory-specific predictions allowing only $\ell$ to freely vary. For such cases, we assume a prior uniform between appropriate ranges on $\ell$, making sure that our marginalized posterior distributions on $\ell$ do not rail over the maximum prior value on $\ell$.

@@

>>>>

In this formalism our QNM frequencies are expressed through functions,
%
\begin{subequations}
\begin{align}
\omega_k &= \omega_k(m_1, m_2, \chi_1, \chi_2,\ell, \{\delta \omega_k^{(j)}\})\\
\tau_k   &= \tau _k(m_1, m_2, \chi_1, \chi_2, \ell, \{\delta \tau_k^{(j)}\})
\end{align}
\end{subequations}
%
where the estimates of $(m_1,\, m_2,\, \chi_1,\, \chi_1)$ are used to predict the final mass and spin $(M_f,\, \chi_f)$ through~\cite{Taracchini:2013rva,Hofmann:2016yih}.
%
Additionally, $(\omega_k,\, \tau_k)$ depend on the coupling constant $\ell$
defined in Eq.~\eqref{eq:def_gamma} as well as the sets, $\{\delta \omega_k^{(j)}\},$ and
$\{\delta \tau_k^{(j)}\}$, where $j$ ranges from zero to the power of spin in Eqs.~\eqref{eq:kerr_expansion}
up to which we include corrections.
%
For example, if we restrict ourselves to corrections in the $j=0$, or $\chi_f^0$, terms for just the $k=(2,2,0)$ mode, then we would just have two additional degrees of freedom, $(\delta \omega_0^{(0)}, \delta \tau_0^{(0)})$. In this paper, we would restrict ourselves to corrections to the $j=0$ and $j=1$ terms, i.e., leading and next-to-leading order corrections to the spin, $\chi_f$.

@@

Just as in GR where the coefficients $\omega^{j}$, $\tau^{j}$ are determined by
comparison against the Kerr QNMs, a theory-specific calculation predicts the
numerical values of $\delta\omega^{(j)}$ and $\delta\tau^{(j)}$
%
This means that using the $\pSEOB$ waveform model with theory-specific informed
QNMs we reduce the parameters space of beyond-GR parameters to one, i.e., to
only $\gamma$, which in turn contains information about the length scale $\ell$.
%
It is important to emphasize that our procedure is different from that of Ref.~\cite{Carullo:2021dui}
which, for a given value of $p$, varied all $\ell$, $\delta\omega^{(i)}$ and $\delta\tau^{(i)}$ parameters.

@@

Among our beyond-GR parameters, $\{\ell, \delta \omega_k^{(j)}\delta \tau_k^{(j)}\}$,
as already mentioned in the previous section, we hold $\{\delta \omega_k^{(j)}\},$
and $\{\delta \tau_k^{(j)}\}$ fixed to theory-specific predictions allowing only $\ell$
to freely vary.
%
For such cases, we assume a prior uniform between appropriate ranges on $\ell$,
making sure that our marginalized posterior distributions on $\ell$ do not rail
over the maximum prior value on $\ell$.

@@

\hs{Quote 90\% credibility results.}
